\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[12pt, a4paper]{book}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{etoolbox}
\usepackage[object=vectorian]{pgfornament}

% 裝飾團案
% https://tex.stackexchange.com/questions/32711/totally-sweet-horizontal-rules-in-latex
\newcommand{\sectionline}{%
  \noindent
  \begin{center}
  {\color{DarkViolet}
    \resizebox{0.5\linewidth}{1ex}
    {{%
    {\begin{tikzpicture}
    \node  (C) at (0,0) {};
    \node (D) at (9,0) {};
    \path (C) to [ornament=85] (D);
    \end{tikzpicture}}}}}%
    \end{center}
  }

\newcommand{\sectionlinetwo}[2]{%
  \nointerlineskip \vspace{.5\baselineskip}\hspace{\fill}
  {\color{#1}
    \resizebox{0.5\linewidth}{2ex}
    {{%
    {\begin{tikzpicture}
    \node  (C) at (0,0) {};
    \node (D) at (9,0) {};
    \path (C) to [ornament=#2] (D);
    \end{tikzpicture}}}}}%
    \hspace{\fill}
    \par\nointerlineskip \vspace{.5\baselineskip}
  }

% 設置引用格式
\AtBeginEnvironment{quote}{\singlespacing\small}

\setlength{\parskip}{5pt}

% 用罗马数字做节的数字
\renewcommand{\thechapter}{\Roman{chapter}.}

\renewcommand*\thesection{\arabic{section}.}
\renewcommand*\thesubsection{}

% 設置頁眉頁腳
\pagestyle{fancy}
\fancyhead{} % clear all fields
\fancyfoot{} % clear all fields

\fancyhead[LE, RO]{\thepage}
\renewcommand\chaptermark[1]{\markboth{#1}{}}
\renewcommand\sectionmark[1]{\markright{ \ #1}}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[RO, RE]{\textit{\rightmark}}
\fancyhead[LE, LO]{\textit{\leftmark}}
\fancyfoot[LE, RO]{\thepage}

% 設置章節標題格式
\titleformat{\chapter}[block]{\centering\Large\bfseries}{\thechapter}{1pt}{\Large}
\titleformat{\section}[block]{\centering\large\bfseries}{\thesection}{1pt}{\large}
\titleformat{\subsection}[block]{\centering\large\bfseries}{\thesubsection}{1pt}{\large}


\title{\textbf{Trades' Unions and Strikes:\\Their Philosophy and Intention}}

\author{T. J. Dunning}
\date{1860}

\begin{document}

     \maketitle

    \begin{center}
        {\LARGE TRADES' UNIONS AND STRIKES}

        \vspace{2em}

        \sectionlinetwo{black}{88}
    \end{center}

    \vspace{2em}

    {\noindent \textsc{The} object of this pamphlet is to obtain a
    hearing on the subject of ``Trades' Unions'' and ``Strikes'' from
    that class who, from their position in society, can only obtain a
    knowledge of it from the evidence of others. In setting forth the
    principle which calls Trade Societies into existence, it is not
    intended to defend all that has been done by Trades' Unions, any
    more than an advocate of religion would attempt to defend all that
    has been done in its name by religious professors. Trades'
    Unionists, generally, are neither writers, nor, to any great extent,
    able to employ writers in their behalf, nor, indeed, to the limited
    extent that they are able, do they at present see the necessity of
    doing so; while, on the contrary, those opposed to them., from their
    wealth and position in society, form a great part of the very class
    by whom writers are directly and indirectly supported;---hence,
    while the press---newspaper and periodical---teems with
    denunciations against them, scarcely a voice, directly from
    themselves, is heard through the press in their behalf Indeed, it
    has been felt by impartial men to be the one great difficulty in the
    way of understanding the subject, that all they can get hold of on
    the matter---except the merely local statements relative to a
    particular strike or dispute, which may then be pending---is
    exclusively on one side. As far as our limited means and power will
    enable us, it is intended by this pamphlet to supply that
    deficiency, by a statement direct from a body of working men, by
    their accredited agent, of their views on the subject.}

    The principal argument against Trades' Unions is professed to be
    derived from the alleged ignorance of the working classes of
    Political Economy. As this term is used by many without having a
    precise idea of what it is, and by different persons in a different
    sense, we will commence by very briefly stating the meaning which we
    attach to it: Political Economy is the science which treats of the
    principle of exchange in its operation in the production of wealth,
    and its operation and influence on civilised society.

    Man is said to be an animal---in contradistinction from all others
   ---that makes exchanges. And it is by the principle of exchange
    that all the transactions of civilised life are carried on, by
    which, indeed, civilised society exists and is held together. But if
    man be an animal that makes exchanges, he undoubtedly retains, in
    common with the carnivora to which he in part belongs, instincts of
    a predatory character, and might be defined to be an animal that,
    besides making exchanges, also steals. The act of exchange embraces
    every conceivable form in which the subject can be treated, and,
    indeed, is that out of which the science itself is evolved. It is
    only necessary, therefore, by analysing this act, to illustrate what
    we understand by the term Political Economy. By the act of exchange,
    the four things essential to a civilised community are supposed,
    without which, indeed, it could not exist, namely.
    \textsc{Labour}---\textsc{Capital}---the right of \textsc{Individual
    Appropriation}, or \textsc{Property}---and \textsc{Security}.
    \textit{Labour}, to produce the thing exchanged; \textit{Capital},
    in the accumulated labour, which results in the article exchanged;
    the recognition of \textit{the right of Individual Appropriation},
    or property, by which the act of exchange takes place, as
    distinguished from the act of taking or keeping possession of the
    article by force; and \textit{Security}, which ensures the peaceful
    continuation of a succession of exchanges to all who have anything
    to dispose of: the result of the whole, in civilised life, being the
    four great classes into which society is divided. Labour yielding
    \textit{wages} giving support to all who labour (using the term in
    its most extensive sense); capital giving \textit{profit}---the
    revenue of those who employ capital. The right of individual
    appropriation, or property, as applied to the land, which, without
    remark, we take as we find it, gives \textit{rent}, which gives
    revenue to landlords. And security supposes \textit{taxes}, which
    support those who defend the country, administer its laws, and
    tax-receivers in general. This last strongly illustrates what is
    very little noticed, if at all, by political economists---namely,
    the predatory instincts of mankind, the omission of which often
    leads to very great error in the application of rules of political
    economy, and to none more than to their application to Trades'
    Unions. And yet these predatory instincts are most unmistakably
    indicated and provided against by this element of exchange,
    security, in the absence of which it certainly could not go on, as
    in communities it requires laws with strong force to support those
    who administer them and enforce their execution, without which the
    community could not exist; and in separate nations, armies and
    fleets for defence, and, as a stronger illustration, for attack. On
    these four elements of the principle of exchange, without either of
    which it could not exist, it will be seen the whole system of
    civilised society rests. We have thus particularised each element,
    and its respective result, to show that those who live by labour
    are, by \textit{right}, entitled to their revenue by the simple
    action of the principle of exchange equally with the other three
    great divisions of society, as opposed to the confused idea of wages
    being derived from the relation of master and servant, involving a
    sort of benevolent patronage on the one side, and obligation on the
    other. And it will be our object to show, that it is only by trade
    combinations that the \textit{free} exercise of this principle can
    be secured to working men.

    Our business, however, is only with the action of the principle of
    exchange upon wages. It is usual, with a certain class of political
    economists, of whom A. Black, Esq., M.P., may be considered a fair
    exponent, to lecture the working classes on the principles of this
    science. Accordingly, in his recent lecture in Edinburgh, he devotes
    five, out of the twenty-two pages it comprises, to the consideration
    of the value of commodities---labour being one in its nature like
    the rest---which is determined by demand and supply; the pernicious
    result of monopoly; of capital and labour, and of each being
    necessary for the employment of the other; that capital will not be
    employed unless a profit can be obtained by its employment; that
    when the profit of capital is high in any trade or manufacture, so
    many will be tempted to embark in it that this high profit will soon
    be reduced to its ordinary level; and the same with high wages,
    except they proceed from great skill, which, from the nature of
    things, must always be rare; and, lastly, if a capitalist has
    embarked his capital upon the supposition that he has to pay a
    certain sum for wages, and he is obliged to pay more, his profit
    will be reduced by that amount, which will be very likely to cause
    him to withdraw from the business in which he has engaged, and, of
    course, cease to pay wages, which should be a lesson to workmen not
    to demand too high wages.

    With due respect for Mr. Black, who doubtless was actuated by a
    sincere desire to promote what he believed to be the true interests
    of the working classes, we think, if, instead of puzzling himself
    and his readers by elaborately explaining the above propositions,
    which nobody is likely to dispute, and which are, in their
    enunciation, like that of two and two making four, already at their
    plainest terms, he had endeavoured to show how it was that these
    things, which almost everybody knows, failed to convince the working
    classes that Trades' Unions are unnecessary, and Strikes always
    pernicious, and shown how they were in error: he would then have
    conferred a real benefit on the working classes. It is a great
    mistake, in gentlemen of Mr. Black's position, to suppose that
    working men are practically ignorant of the truths of political
    economy. With it as a science they may be ignorant; indeed, some of
    them may not even know that there is such a science. But these
    gentlemen seem to forget that political economy is only the
    compilation into a code of rules the practice of all men in all ages
    who have bought and sold; have been engaged in commercial
    transactions; or in any way have made use of the principle of
    exchange. Every costermonger is obliged to regulate what he does in
    buying and selling by the law of demand and supply, which if
    explained to him as being a part of the science of political
    economy, he would be as much surprised that he had, without knowing
    it, been practising the science all his life, as the honest
    gentleman in the French comedy was, on his being taught composition,
    that he had been talking prose all his life without knowing it.
    Except in the innocent dulness of the latter, which would certainly
    not belong to the costermonger, the cases are exactly parallel.

    We therefore will endeavour to show why the above propositions fail
    in convincing working men that they are doing wrong in entering into
    combination. Not that these propositions arc doubted, but because
    implicit belief in them is perfectly consistent with the propriety
    of Trade Combinations. We shall therefore proceed to consider ---

    \begin{enumerate}[label=\Roman*., leftmargin=2.9cm]
        \item---Wages, and what determines their value.
        \item---Trade Societies, for the protection of wages.
        \item---The means used by them for that purpose.
    \end{enumerate}

    \include{wages}
    \include{trade_societies}
    \include{strikes}

\end{document}
